---
title: "prediction.rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading student files for prediction activity

``` {r}
library(tidyverse)
info_df <- read_csv("../Resources/studentInfo.csv")
head(info_df, 3)
```

``` {r}
assessment_df <- read_csv("../Resources/studentAssessment.csv")
head(assessment_df, 3)
```

``` {r}
vle_df <- read_csv("../Resources/studentVle.csv")
head(vle_df,3)
```

### Wrangling
* Calculate the average daily number of clicks (site interactions) for each student from the `studentVle` dataset
* Calculate the average assessment score for each student from the `studentAssessment` dataset
* Merge your click and assessment score average values into the the `studentInfo` dataset

``` {r}
info_df
```

``` {r}
studentgrouped_vle <- vle_df %>% group_by(id_student)
vle_merge <- summarize(studentgrouped_vle, avg_click=round(mean(sum_click)))
head(vle_merge,3)
```


``` {r}
studentgrouped_assess <- assessment_df %>% group_by(id_student)
assess_merge <- summarize(studentgrouped_assess, avg_score=round(mean(score)))
head(assess_merge, 3)
```

``` {r}

merge_df <- merge(vle_merge,assess_merge,by="id_student",all=TRUE)
merge_df
```

``` {r}
allmerge_df <- merge(info_df, merge_df, by="id_student", all=TRUE)
allmerge_df
```

### Create a Validation Set
* Split your data into two new datasets, `TRAINING` and `TEST`, by **randomly** selecting 25% of the students for the `TEST` set
sample_n(allmerge_df, (length(allmerge_df)*.75))

``` {r}
n <- nrow(allmerge_df)
trainIndex <- sample(1:n, size = round(0.75*n), replace=FALSE)
train <- allmerge_df[trainIndex ,]
test <- allmerge_df[-trainIndex ,]
```

### Explore
* Generate summary statistics for the variable `final_result`
* Ensure that the final_result variable is binary (Remove all students who withdrew from a courses and convert all students who recieved distinctions to pass)
* Visualize the distributions of each of the variables for insight
* Visualize relationships between variables for insight

``` {r}
filtered_result <- filter(allmerge_df, final_result != "Withdrawn")
filtered_result <- filtered_result %>% mutate_if(is.character, str_replace_all, pattern = 'Distinction', replacement = 'Pass')
pass_fail <- filtered_result %>% group_by(final_result)
summarize(pass_fail, n())
```

``` {r}

```



