---
title: "4051_predi_act"
author: "Ruiqi Wang"
date: "February 11, 2020"
output: html_document
---

```{r}
library(readr)
Vle <- read_csv("studentVle.csv")
Ass <- read_csv("studentAssessment.csv")
Info <- read_csv("studentInfo.csv")
```

#Calculate the average daily number of clicks (site interactions) for each student from the studentVle dataset
```{r}
library(tidyr)
library(lsa)
library(dplyr)
avg <- select(Vle, "id_student", "date", "sum_click");
avg <- arrange(avg, id_student)
daily <- aggregate(avg[, 3], list(avg$id_student), mean)
```


#Calculate the average assessment score for each student from the studentAssessment dataset
```{r}
ass <- select(Ass, "id_student", "score");
ass <- arrange(ass, id_student)
avg_assess <- aggregate(ass[, 2], list(ass$id_student), mean)
```


#Merge your click and assessment score average values into the the studentInfo dataset
```{r}
names(daily)[1] <- "id"
m1 <- merge(Info, daily, by.x="id_student", by.y = "id")
names(avg_assess)[1] <- "id"
m1 <- merge(m1, avg_assess, by.x="id_student", by.y = "id")
```
#Create a Validation Set
#Split your data into two new datasets, TRAINING and TEST, by randomly selecting 25% of the students for the TEST set
```{r}
#install.packages("caret")
#library(caret) 
#trainData <- createDataPartition(
#  y = data$thing,
#  p = .75,
#  list = FALSE)
```
#Explore
#Generate summary statistics for the variable final_result
```{r}
```
#Ensure that the final_result variable is binary (Remove all students who withdrew from a courses and convert all students who recieved distinctions to pass)
```{r}
```
#Visualize the distributions of each of the variables for insight
```{r}
```
#Visualize relationships between variables for insight
```{r}
```
#Model Training
```{r}
```
#Install the caret package
```{r}
```
#You will be allocated one of the following models to test:

#CART (RPART), Conditional Inference Trees (party), Naive Bayes (naivebayes), Logistic Regression (gpls)
```{r}
```
#Using the trainControl command in the caret package create a 10-fold cross-validation harness:
#control <- trainControl(method="cv", number=10)
```{r}
```
#Using the standard caret syntax fit your model and measure accuracy:
#fit <- train(final_result~., data=TRAINING, method=YOUR MODEL, metric="accuracy", trControl=control)
```{r}
```
#Generate a summary of your results and create a visualization of the accuracy scores for your ten trials
```{r}
```
#Make any tweaks to your model to try to improve its performance
```{r}
```
#Model Testing
#Use the predict function to test your model
#predictions <- predict(fit, TEST)
#Generate a confusion matrix for your model test
#confusionMatrix(predictions, TEST$final_result)
